{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-23 Paper/main.tex
Monomial basis & Fourier Basis

	\begin{equation}
		f(t) = \sum_{k =1}^{K} c_k(t -w)^{k-1}
	\end{equation}
	can be expressed as a linear combination of the monomials $(t - w)$ which form the basis

	\begin{equation}
		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
	\end{equation}

	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.

	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase. This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		S_{i}^{FB}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	{\color{orange}$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup
	\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$}

	\begin{figure}[H]\label{fourier_basis}
	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
	\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}

@@

    \begin{equation}
    	\begin{split}
    		f_2(t) = & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)}
    	\end{split}
    \end{equation}
    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. 
    Both functions were created such that the inner product $\langle NIR_{sim}, f \rangle, f \in \{f_1(t), f_2(t)\}$ creates responses similar to the original octane ratings of the gasoline dataset.

@@

		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios and are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$.

@@

		where $Z \sim \mathcal{N}(0,1)$ to test the methods with different signal-to-noise ratios. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with different number of cubic bspline basis-function $(5,6,...,25)$ and fourier functions $(1,2,...,25)$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used 10f cross-validation. The simulation was done with R (version...). We carried out 2500 repetitions for each set of simulations. {\color{green} Information about version and link to repo / package in footnote??}

	\subsection{Put in appendix - Simulation setup cont.}

	The

	\subsection{Results}

>>>>

	\begin{equation}
		f(t) = \sum_{k =0}^{K} c_k(t -w)^{k}
	\end{equation}
	can be expressed as a finite linear combination of the monomials $(t - w)^{k}$ with coefficient $c_k$ which form the basis

	\begin{equation}
		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
	\end{equation}
	The single basis function $1$ within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}).\\
	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
	 Problems of collinearity arise for higher degrees since the monomial basis becomes more correlated as the degrees increase. This restricts the number of degrees and therefore the use of this basis: For simple functions this may be useful, but the small number of degrees makes it impossible to capture pronounced local peculiarities and leads to undesirable behaviour at the tails. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	The Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		S_{i}^{FB}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	{\color{orange}$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup
	\{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$}
	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthogonal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.  
	\begin{figure}[H]\label{fourier_basis}
	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
	\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}

@@

    \begin{equation}
    	\begin{split}
    		f_2(t) = & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)}
    	\end{split}
    \end{equation}
    \vspace{0.2cm}\\

    The bumpy function, $f_2(t)$, was generated by referring to \cite{cardot_bumpyfunction_2002}. 
    Both functions were created such that the inner product $\langle NIR_{sim}, f \rangle, f \in \{f_1(t), f_2(t)\}$ creates responses similar to the original octane ratings of the gasoline dataset.

@@

		 Two different error-terms $\epsilon$ were created by first generating an $i.i.d.$ standard normal error term and then multiplying it by two error variations $\sigma_e $. The error variations represent different signal-to-noise ratios to test the methods both with a low and a high amount of noise. They are created such that the squared multiple correlation coefficient $R^2 = var(Xf) / (var(Xf) + \sigma^2_{e})$ is equal to 0.9 and 0.6. The two error-terms are then used to generate two sets of responses for $f \in \{f_1(t), f_2(t)\}$

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 5\}$, cubic bspline basis-function $\{5,6,...,25\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used 10 fold cross-validation. The simulation was done with R (version...). In total we conducted out 2500 repetitions for each set of simulations. {\color{green} Information about version and link to repo / package in footnote??}

	\subsection{Results}
	DESCRIBE RESULTS
